My title

### 2022-02-27 outputs/paper/paper.Rmd
Auto stash before merge of "huakun" and "origin/main"

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Replication avaliable at https://doi.org/10.48152/ssrp-mbxx-jm47. Code and data avaliable at https://github.com/cuilantao/STA304-Paper-2"         
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper is based on Kearney's paper The Puzzle of Falling US Birth Rates since the Great Recession Between 1980. ^[Original paper available at: https://www.aeaweb.org/articles?id=10.1257/app.2.2.95] [@cite_original] During the Great Recession, US birth rate varied between a tight range of roughly 65 to 70 birth per 1000 women between the age of 15 to 44. However, after the Great Recession, the birth rate started to decline significantly, it dropped by nearly 20 percent in 13 years. In this paper, we aim to find out the reason behind the decline, all of the data are collected from the CDC Vital Statistics Births Reports. Our findings can help to understand the reason behind the drop. "
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Replication avaliable at https://doi.org/10.48152/ssrp-mbxx-jm47. Code and data avaliable at https://github.com/cuilantao/STA304-Paper-2"         
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper is based on Kearney's paper The Puzzle of Falling US Birth Rates since the Great Recession Between 1980. ^[Original paper available at: https://www.aeaweb.org/articles?id=10.1257/app.2.2.95] [@cite_original] During the Great Recession, US birth rate varied between a tight range of roughly 65 to 70 birth per 1000 women between the age of 15 to 44. However, after the Great Recession, the birth rate started to decline significantly, it dropped by nearly 20 percent in 13 years. In this paper, we aim to find out the reason behind the decline, all of the data are collected from the CDC Vital Statistics Births Reports. Our findings can help to understand the reason behind the drop. "
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
header-includes:
  - \usepackage{subfig}
---

@@

## LGBT Section

The percentage of LGBT (and many other genders) has risen in recent years in the US, probably related to propaganda and political correctness.

Since there is not much data for other genders, and LGBT are the majorities, we will focus on LGBT population and the potential effect they bring to birth rate.

LGBT is the acronym of the following 4 genders, **L** for Lesbian, **G** for gay, **B** for bisexual, **T** for transgender. By definition, these genders by definition should have a much lower birth rate than heterosexual. Thus, the population changes in these population are very likely to make an impact on the birth rate of the US.

```{r echo = FALSE, fig-gender-raising-children-distribution, fig.cap='Gender Distribution and Percentage Raising Children Distribution', fig.subcap=c('LGBT Gender Distribution', 'LGBT Percentage Raising Children', 'Same Sex Couple Gender Distribution'), out.width='.33\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c("./images/LGBT-Gender-distribution.png",
  "./images/LGBT-percentage-raising-children.png",
  "./images/same-sex-couple-gender-distribution.png"))
```

Figure \@ref(fig:fig-gender-raising-children-distribution) shows the gender distribution of LGBT and Same Sex Couple as well as the percentage raising children.
Figure \@ref(fig:fig-gender-raising-children-distribution) (a) and Figure \@ref(fig:fig-gender-raising-children-distribution) (c) clearly shows that more females are non-heterosexual.
This should make a even larger impact on birth rate as only females are able to give births (in normal situations).

Figure \@ref(fig:fig-gender-raising-children-distribution) (b) shows the percentage of LGBT population that raise children. 71% of the LGBT population don't raise children. With these information, we can conclude that the growth of LGBT population is able to cause a negative change in birth rate.

```{r echo = FALSE, fig-density-state, fig.cap='Density by State', fig.subcap=c('Same Sex Couple State Density', 'LGBT State Density', 'Birth Rate Distribution by State'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/same-sex-couple-state-density.png", "./images/LGBT-state-density.png", "./images/state-birth-rate-distribution.png"))
```

Figure \@ref(fig:fig-density-state) shows the population density of Same Sex Couple and LGBT by States, and birth rate distribution by State. Darker color means higher density or higher negative change in birth rate. From these plots we can see that the states with higher LGBT density and same sex couples generally have higher negative change in birth rate. We cannot conclude whether LGBT population has a large impact on US birth rate based on these plots yet, but there should be some correlation between birth rate and gender identity of Americans.

[@cite_original]

```{r echo = FALSE, fig-race-distribution, fig.cap='Race Distribution', fig.subcap=c('Same Sex Couple Race Distribution', 'LGBT Race Distribution'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2, fig.align="center"}
knitr::include_graphics(c("./images/same-sex-couple-race-distribution.png", "./images/LGBT-race-distribution.png"))
```

```{r echo = FALSE, fig-age-distribution, fig.cap='LGBT and Same Sex Couple Age Distribution', fig.subcap=c('Same Sex Couple Race Distribution', 'LGBT Race Distribution'), out.width='.40\\linewidth', fig.asp=1, fig.ncol = 2, fig.align="center"}
knitr::include_graphics(c("./images/same-sex-couple-age-distribution.png", "./images/LGBT-age-distribution.png"))
```

```{r echo = FALSE, fig-LGBT-socioeconomic-indicators, fig.cap='LGBT Socioeconomic Indicators', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/LGBT-socioeconomic-indicators.png")
```
